Combining information from photometric and spectroscopic data:\\ Probabilistic spectrophotometric inference

### 2015-07-06 tex/figures.tex
plotting for n_phot trials, more plot prettification

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/specphot_uncalibrated.pdf}
\caption{Joint Posterior PDFs for the calibration parameters inferred
from the combination of \emph{uncalibrated} spectroscopy and all the
photometric data points.
\label{fig:cal_posterior}}
\end{figure*}

@@

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
\caption{The value of more photometry. Marginalized posterior PDFs
obtained from mock spectra and photometry, for different numbers of
photometric bands.  The pdfs $g$-band only ({\it red}), $g$- and $i-$
band ({\it blue}), and the combined SDSS $griz$ and 2MASS $JHK_s$ set of
bands ({\it orange}).
\label{fig:vary_phot}}
\end{figure*}

@@

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/inferred_calibration.pdf}
\caption{Left: Ratio of the calibration vector inferred from the
  real uncalibrated spectrum to that inferred from the real calibrated
  spectrum ({\it green}). Taking the ratio reduces the effects of model
  imperfections and shows how well we are able to infer the
  calibration vector of \citet{schiavon05} ({\it black}).  
Right: Joint posterior PDFs for the inferred calibration parameters.
\label{fig:real_calibration_ratio}}
\end{figure*}

>>>>

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/calibration_posterior.pdf}
\caption{Joint Posterior PDFs for the calibration parameters inferred
from the combination of \emph{uncalibrated} spectroscopy and all the
photometric data points.
\label{fig:cal_posterior}}
\end{figure*}

@@

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/vary_nphot.pdf}
\caption{The value of more photometry. Marginalized posterior PDFs
obtained from mock spectra and photometry, for different numbers of
photometric bands.  The pdfs $g$-band only ({\it red}), $g$- and $i-$
band ({\it blue}), and the combined SDSS $griz$ and 2MASS $JHK_s$ set of
bands ({\it orange}).
\label{fig:vary_phot}}
\end{figure*}

@@

%\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/inferred_calibration.pdf}
%\caption{Left: Ratio of the calibration vector inferred from the
%  real uncalibrated spectrum to that inferred from the real calibrated
%  spectrum ({\it green}). Taking the ratio reduces the effects of model
%  imperfections and shows how well we are able to infer the
%  calibration vector of \citet{schiavon05} ({\it black}).  
%Right: Joint posterior PDFs for the inferred calibration parameters.
%\label{fig:real_calibration_ratio}}
%\end{figure*}
